### 2013-11-05 inst/examples/policycosts/plot_table.Rmd
update plot, smaller table

df3$reduction <- as.factor(df3$reduction)
#ggplot(df3) + geom_line(aes(sigma_g, value, col=penalty_fn, lty=variable)) + facet_wrap(~reduction) 
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn) 
```

```{r results="asis"}
print(xtable::xtable(df3), type="html")
```

>>>>

df3$reduction <- as.factor(df3$reduction)
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
```

```{r results="asis"}
print(xtable::xtable(df), type="html")
```
